The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-02-02 paper.tex
update

\section{Introduction}
Over the last decade the discovery of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
the high resolution X-ray map \citep{Predehl2020} from eROSITA \citep{Predehl2021} also shows\
similar X-ray bubbles above and below the Galaxy,\
but about twice as large as the Fermi bubbles, each having a diameter of about 45,000 lightyears.\

The \textit{Fermi} and eROSITA bubbles, two couple giant bubbles extending about 50 degrees\
above and below the Galactic center (GC),\
are among the most important findings of the Fermi Gamma-ray Space Telescope\

The Fermi bubbles and large-scale X-ray emission revealed by eROSITA\
show remarkable morphological similarity.

>>>>

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two giant bubbles symmetrically extending about 50 degrees above and below the Galactic center,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

The gamma-ray emission of the Fermi bubbles is observed in the energy range\
of $1\lesssim E_{\gamma} \lesssim 100$ GeV and has an almost spatially uniform hard\
spectrum, sharp edges and an approximately flat brightness distribution.\

Over the course of a decade,\
the first all-sky survey X-ray data with high-spatial resolution \citep{Predehl2021}\
from eROSITA \citep{Predehl2020} also reveals\
a large hourglass-shaped structure (eROSITA bubbles, hereafter) at the GC,\
symmetrically extending about 80 degress above and below GC.

The large-scale X-ray structure\
shows that the intrinsic size of the bubbles is 14 kiloparsecs across \citep{Predehl2021},
and has remarkable morphological similarities to the Fermi bubbles.

The Fermi and eROSITA bubbles (collectiely we called the Galactic bubbles)
